---
title: "WordCloud With R"
author: "Armand"
date: "1 de mayo de 2017"
output: html_document
---

#We will make a wordcloud from a txt document
###The document is the speech of the Infamous Venezuelan President Nicolás Maduro in Cuba on  November 30, 2016

##Load the packages
```{r}
suppressWarnings(library(tm)) #Text mining 
suppressWarnings(library(wordcloud))# WordCloud
suppressWarnings(library(RColorBrewer)) # Colors


```

##Read the file
```{r}
myfile <- suppressWarnings(paste(readLines('file.txt'), collapse=" "))

```

##Formanting and cleanind the data
```{r}
df1 <- data.frame(c(myfile))
df1 <- DataframeSource(df1)
#df1 <- DataframeSource(textto)
#head(df1)


###change df1 to Corpus
corps <- Corpus(df1)
##Remove Punctuation
corps <-tm_map(corps, removePunctuation)
##Change to lower case
corps <- tm_map(corps, tolower)
#Remove Numbers
corps <- tm_map(corps, removeNumbers)
#Remove words in spanish like 'a' 'de' 'lo' etc
corps <- tm_map(corps, removeWords, stopwords('spanish'))
#Corpt to Text
corps <- tm_map(corps, PlainTextDocument)
##Matrix
matrix.ter <- TermDocumentMatrix(corps)
matrix.ter <- as.matrix(matrix.ter)
head(matrix.ter)


```


##Change the df to vector
```{r}
####Vector
vector.ter <- sort(rowSums(matrix.ter), decreasing=TRUE)
head(vector.ter)

dataframe.ter <- data.frame(word =names(vector.ter), freq=vector.ter)


```

##This dataframe will be use to build the wordcloud
```{r}
## Finally this dataframe will be use to build the wordcloud
head(dataframe.ter)


```



##Finally, we Make the graph

```{r}
suppressWarnings(wordcloud(dataframe.ter$word, dataframe.ter$freq, scale=c(8,.2), min.freq=3, max.words=Inf, random.order=FALSE,rot.per=.15, colors=brewer.pal(8,"Dark2")))


```


##Conclusion:
###Nothing new the main words are: Chavez and Fidel.
