---
title: "Visualization Examples"
author: "Armand"
date: "18 de julio de 2016"
output: html_document
---


##Example qplot

```{r}
library(ggplot2)
qplot(mpg, cyl, data = mtcars, col = as.factor(hp))
```

##Change the theme

```{r}
qplot(mpg, cyl, data = mtcars, col = as.factor(hp)) + theme_bw(15)

```


##Change the Position of legend

```{r}
qplot(mpg, cyl, data = mtcars, col = hp) + theme( legend.position= "bottom")

```


##Changing the element

```{r}
qplot(mpg, vs, data = mtcars, col = as.factor(vs), shape = as.factor(vs)  ) + theme( legend.position= "bottom")

```

##Adding name to legend

```{r}

qplot(mpg, vs, data = mtcars, col = as.factor(vs), shape = as.factor(vs)  ) + theme( legend.position= "bottom")+ scale_shape_discrete(name = "vs") + scale_color_discrete(name ="VS2")
```

#ggplot examples

```{r}

ggplot(iris, aes( x=Sepal.Length, y = Petal.Length)) + geom_point() + scale_x_continuous("Longitud")

```


##Changing colors and shapes

```{r}
ggplot(iris, aes( x=Sepal.Length, y = Petal.Length, shape =Species, color = Species)) + geom_point()  + scale_x_continuous("Longitud")

```


##Adding curve to data:

```{r}

ggplot(iris, aes( x=Sepal.Length, y = Petal.Length, shape =Species, color = Species)) + geom_point()  + scale_x_continuous("Longitud") + geom_smooth(se = FALSE)

```


##Adding only 1 curve

```{r}

ggplot(iris, aes( x=Sepal.Length, y = Petal.Length, shape ="p", color = "pink")) + geom_point()  + scale_x_continuous("Longitud") + geom_smooth(se = TRUE)

```

##Quitting the points and plotin smooth with regression method

```{r}

ggplot(iris, aes( x=Sepal.Length, y = Petal.Length, color = "pink"))   + scale_x_continuous("Longitud") + geom_smooth(se = TRUE, method = lm)


```


##Adding the points

```{r}

ggplot(iris, aes( x=Sepal.Length, y = Petal.Length, color = "pink")) + geom_point()  + scale_x_continuous("Longitud") + geom_smooth(se = TRUE, method = lm)

```

##Faceting with ggplot:

```{r}

ggplot(iris, aes( x=Sepal.Length, y = Petal.Length, shape =Species, color = Species)) + geom_point()  + scale_x_continuous(" Sepal Length ")+ scale_y_continuous("Petal Length") + geom_smooth(se = FALSE, method = lm) + facet_wrap(~Species)+ ggtitle("Relationship Between Sepal Lenght vs Petal length")  

```


##Plotting histogram:

```{r}

ggplot(iris, aes( x=Sepal.Length )) + geom_histogram(binwidth = .5, colour="black", fill ="white")  + scale_x_continuous(" Sepal Length ")+ scale_y_continuous("Petal Length") + ggtitle("Relationship Between Sepal Lenght vs Petal length") 

```

##Plotting Horizontal Histogram:

```{r}

ggplot(iris, aes( x=Sepal.Length )) + geom_histogram(binwidth = .5, colour="black", fill ="white")  + scale_x_continuous(" Sepal Length ")+ scale_y_continuous("Petal Length") + ggtitle("Relationship Between Sepal Lenght vs Petal length") + coord_flip()

```

##Adjusting the facets scales

```{r}

ggplot(iris, aes( x=Sepal.Length, y = Petal.Length, shape =Species, color = Species)) + geom_point()  + scale_x_continuous(" Sepal Length ")+ scale_y_continuous("Petal Length") + geom_smooth(se = FALSE, method = lm) + facet_wrap(~Species, scale="free_y")+  ggtitle("Relationship Between Sepal Lenght vs Petal length") 

```



Plotting Density:

```{r}
ggplot(iris, aes( x=Sepal.Length )) + geom_density()  + scale_x_continuous(" Sepal Length ")+ scale_y_continuous("Petal Length") + ggtitle("Relationship Between Sepal Lenght vs Petal length")

```

##Filling Densities plots:
```{r}

ggplot(iris, aes( x=Sepal.Length, fill =as.factor(Species) )) + geom_density()  + scale_x_continuous(" Sepal Length ")+ scale_y_continuous("Petal Length") + ggtitle("Relationship Between Sepal Lenght vs Petal length")+ scale_fill_discrete(name = "Species")

```


##Adding color to lines in density graphs

```{r}

ggplot(iris, aes( x=Sepal.Length, color =as.factor(Species) )) + geom_density()  + scale_x_continuous(" Sepal Length ")+ scale_y_continuous("Petal Length") + ggtitle("Relationship Between Sepal Lenght vs Petal length")+ scale_fill_discrete(name = "Species")

```



##Box plot

```{r}

ggplot(iris, aes( x=Sepal.Length, y = Petal.Length, group = Sepal.Length )) + geom_boxplot() + ggtitle("Relationship Between Sepal Lenght vs Petal length")

```



##Violin Graphs:

```{r}

ggplot(data = iris, aes(x =(Sepal.Length) , y = Sepal.Length)) + geom_violin() + ggtitle("Relationship Between Sepal Lenght vs Petal length")

```


##Adding text with ggplot:
```{r}

ggplot(data = mtcars, aes(wt , mpg, label = row.names(mtcars))) + geom_point()+ ggtitle("Relationship Between Sepal Lenght vs Petal length")+ geom_text()

```


##Cheking overlap:

```{r}

ggplot(data = mtcars, aes(wt , mpg, label = row.names(mtcars))) + geom_point()+ ggtitle("Relationship Between Sepal Lenght vs Petal length")+ geom_text( check_overlap = TRUE)

```

