---
title: "Big data with R"
author: "Armand"
date: "29 de julio de 2016"
output: html_document
---

#Exploring some packages for big data with R


###Read Data From file to ff

load the package
```{r}
suppressMessages(library(ff))
suppressMessages(library(ffbase))
suppressMessages(library(biglm))

```


```{r}
datos <- read.csv.ffdf(file="SAheart.csv", sep=",", header =T, dec =".", row.names=1)
head(datos)
```

```{r}
str(datos)

```

#Regression with Biglm

```{r}
model <- bigglm(tobacco~ldl, data = datos)
summary(model)

```

Prediction
```{r}
pred <- predict(model, newdata = data.frame(tobacco=c(1.2, 45.8, 100.32), ldl = c(2, 0.24, 0.002)))
pred


```
It can be done with multiple vars

#Parallel Computing

```{r}
#load packages snow
suppressMessages(library(snow))
suppressMessages(library(MASS))
```

Load the data

```{r}

dataf <- read.csv("EjemploClientes.csv", header = TRUE, sep = ";", dec = ",", row.names = 1)
head(dataf)

```
Normalized the age by dividin by 10
```{r}
dataf$Edad <- dataf$Edad/10
head(dataf)

```

```{r}
groups <- kmeans(dataf, 4, iter.max = 100, nstart = 100)
groups

```

inertia
```{r}
groups$tot.withinss

```

##Using SNOW for parallelism
using lapplay 
```{r}
clust <- makeCluster(2, type = "SOCK")#2 is for amount of cpu's
ignore <- clusterEvalQ(clust, {
  library(MASS)#load mass to every worker node
  NULL
})

```


apply the snow
```{r}
#clust = cluster, 30 = inpust, function = function to be applied
result <- clusterApply(clust, c(30,30, 30, 30), function(n) kmeans(Boston, 4, nstart = n))
result

```

Inertias
```{r}
iner <- sapply(result, function(result) result$tot.withinss)
iner
```
the best result
```{r}
result <- result[[which.min(iner)]]
result
```
stop the clusters
```{r}
stopCluster(clust)

```



#Compare sequential vs parallel time with kmeans 

For sequential
```{r}
time1 <- system.time( groups <- lapply(c("Hartigan-Wong","Lloyd","Forgy", "MacQueen"), function(algorit) kmeans(dataf, 3, iter.max = 30000000, nstart = 100000, algorithm = algorit)))
for (i in 1:4) {
  print(groups[[i]]$betweenss)
}

```

Parallel

```{r}
clust <- makeCluster(2, type = "SOCK")#2 is for amount of cpu's
ignore <- clusterEvalQ(clust, {
  dataf <- read.csv("EjemploClientes.csv", header = TRUE, sep = ";", dec = ",", row.names = 1)
  dataf$Edad <- dataf$Edad/10#load mass to every worker node
  NULL
})

time2 <- system.time( groups <- clusterApply(clust, c("Hartigan-Wong","Lloyd","Forgy", "MacQueen"), function(algorit) kmeans(dataf, 3, iter.max = 30000000, nstart = 100000, algorithm = algorit)))
for (i in 1:4) {
  print(groups[[i]]$betweenss)
}

stopCluster(clust)
```

```{r}
#Sequential Time:
time1

```

```{r}
#Parallel Time
time2

```

