---
title: "Box-Jenkins"
author: "Armand"
date: "22 de julio de 2016"
output: html_document
---


##White Noise

```{r}

q <- rnorm(100, 0,1)
q

```

plotting the noise

```{r}
par(mfrow=c(2,1))
ts.plot(q)
panel.first=grid()
panel.first=grid()
acf(q, main="Autocorrelation simple")
panel.first=grid()

```

density
```{r}
plot(density(q))

```



###Random walk
Example
```{r}
w <- rnorm(100) # w N(0,1)
x <- w
for (t in 2:100) {
  x[t]<- x[t-1]+w[t]
}

par(mfrow=c(2,2))
ts.plot(x, main="Random Walk x_t")
acf(x, main="Autocorrelation simple xt")
d <- diff(x) # differences of xs
ts.plot(d, main ="first Difference of x_t")
acf(d, main ="Autocorrelation simple of D", ylim = c(-1,1), ci.col="blue")
```


##Autoregressive (AR) model 
order 1
```{r}

layout(matrix(c(1,1,2,3),2,2, byrow=TRUE))
#arima model
AR <- arima.sim(n=100, model =list(order =c(1,0,0), ar =0.4))
plot(AR, main =(expression(AR(1)~~~~phi==+0.4)))
acf(AR, main ="Simple Autocorrelation", ylim = c(-1,1), col ="black")
pacf(AR, main ="Partial Autocorrelation", ylim = c(-1,1), col ="black")
```


order 2
```{r}

layout(matrix(c(1,1,2,3),2,2, byrow=TRUE))
#arima model
AR <- arima.sim(n=100, model =list(order =c(2,0,0), ar =c(0.8897,-0.4858)))
plot(AR, main =(expression(AR(2)~~~~phi==c(0.8897,-0.4858))))
acf(AR, main ="Simple Autocorrelation O2", ylim = c(-1,1), col ="black")
pacf(AR, main ="Partial Autocorrelation O2", ylim = c(-1,1), col ="black")
```



#Moving Average

Example order 1

```{r}

layout(matrix(c(1,1,2,3),2,2, byrow=TRUE))
#arima model
AR <- arima.sim(n=100, list(order =c(0,0,1), ma =1))
plot(AR, main =(expression(MA(1)~~~~theta==+1)))
acf(AR, main ="Simple Autocorrelation O1", ylim = c(-1,1), col ="black")
pacf(AR, main ="Partial Autocorrelation O1", ylim = c(-1,1), col ="black")
```



Example order 2

```{r}

layout(matrix(c(1,1,2,3),2,2, byrow=TRUE))
#arima model
AR <- arima.sim(n=100, list(order =c(0,0,2), ma =c(0.7,0.3)))
plot(AR, main =(expression(MA(2)~~~~theta==c(0.7,0.3))))
acf(AR, main ="Simple Autocorrelation O2", ylim = c(-1,1), col ="black")
pacf(AR, main ="Partial Autocorrelation O2", ylim = c(-1,1), col ="black")
```


##With lake data
###ARMA Models

```{r}
data("LakeHuron")

```

Build ARMA(1,1)
```{r}
model <- arima(LakeHuron, order = c(1,0,1))
pred <- predict(model, n.ahead = 8)#predict 8 data in time
pred

```

###plotting Data

```{r}

layout(matrix(c(1,1,2,3),2,2, byrow=TRUE))
plot(LakeHuron, xlim = c(1875, 1980), ylim = c(575,590), type ="o")
lines(pred$pred, col ="red", type ="o")
lines(pred$pred+2*pred$se, col ="green3", lty =2, type ="o")
lines(pred$pred-2*pred$se, col ="purple", lty =3, type ="o")
acf(AR, main ="Simple Autocorrelation O1", ylim = c(-1,1), col ="black")
pacf(AR, main ="Partial Autocorrelation O1", ylim = c(-1,1), col ="black")
```

###Model order 2

Build ARMA(2,1)
```{r}
model <- arima(LakeHuron, order = c(2,0,1))
pred <- predict(model, n.ahead = 8)#predict 8 data in time
pred

```


###plotting Data

```{r}

layout(matrix(c(1,1,2,3),2,2, byrow=TRUE))
plot(LakeHuron, xlim = c(1875, 1980), ylim = c(575,590), type ="o")
lines(pred$pred, col ="red", type ="o")
lines(pred$pred+2*pred$se, col ="green3", lty =2, type ="o")
lines(pred$pred-2*pred$se, col ="purple", lty =3, type ="o")
acf(AR, main ="Simple Autocorrelation O1", ylim = c(-1,1), col ="black")
pacf(AR, main ="Partial Autocorrelation O1", ylim = c(-1,1), col ="black")
```


### Now Arma(2,2)

```{r}
model <- arima(LakeHuron, order = c(2,0,2))
pred <- predict(model, n.ahead = 8)#predict 8 data in time
pred

```



###plotting Data

```{r}

layout(matrix(c(1,1,2,3),2,2, byrow=TRUE))
plot(LakeHuron, xlim = c(1875, 1980), ylim = c(575,590), type ="o")
lines(pred$pred, col ="red", type ="o")
lines(pred$pred+2*pred$se, col ="green3", lty =2, type ="o")
lines(pred$pred-2*pred$se, col ="purple", lty =3, type ="o")
acf(AR, main ="Simple Autocorrelation O1", ylim = c(-1,1), col ="black")
pacf(AR, main ="Partial Autocorrelation O1", ylim = c(-1,1), col ="black")
```


#ARIMA(p,d,q) Model

Load Library
```{r}
suppressMessages(library(forecast))

```

This function suggest parameters
```{r}
auto.arima(LakeHuron)


```


the model with the parameters suggested
```{r}
model <- arima(LakeHuron, order = c(0,1,4))
pred <- predict(model, n.ahead = 8)#predict 8 data in time
pred

```



###plotting Data

```{r}

layout(matrix(c(1,1,2,3),2,2, byrow=TRUE))
plot(LakeHuron, xlim = c(1875, 1980), ylim = c(575,590), type ="o")
lines(pred$pred, col ="red", type ="o")
lines(pred$pred+2*pred$se, col ="green3", lty =2, type ="o")
lines(pred$pred-2*pred$se, col ="purple", lty =3, type ="o")
acf(AR, main ="Simple Autocorrelation O1", ylim = c(-1,1), col ="black")
pacf(AR, main ="Partial Autocorrelation O1", ylim = c(-1,1), col ="black")
```



#ARMIA(p,d,q)(P,D,Q)

With periodgram
```{r}
layout(1,1)
res.per <- spec.pgram(LakeHuron, log ="no")

```

Sort the Data
```{r}
order( res.per$spec, res.per$freq, decreasing = T)

```

The point are  3, 13 and 9

The frecuency at given points
```{r}

max1 <- res.per$freq[3]
max2 <- res.per$fre[13]
max3 <- res.per$fre[9]
```

Adding the lines
```{r}
res.per <- spec.pgram(LakeHuron, log ="no")
abline(v=max1, lty=3, col = 2)
abline(v=max2, lyt =3, col=3)
abline(v=max3, lty = 3, col = 4)
```


###The periods are
Period 1
```{r}
period1 <- 1/max1
period1
```

Period 2
```{r}
period2 <- 1/max2
period2
```

Period 3
```{r}
period3 <- 1/max3
period3
```



#Buildind arima model
give the period = 11 to the model
```{r}
model <- arima(LakeHuron, order=c(1,2,1), seasonal = list(order=c(2,1,0), period=11))
pred <- predict(model, n.ahead = 8)
pred

```

###plotting Data

```{r}

layout(matrix(c(1,1,2,3),2,2, byrow=TRUE))
plot(LakeHuron, xlim = c(1875, 1980), ylim = c(575,590), type ="o")
lines(pred$pred, col ="red", type ="o")
lines(pred$pred+2*pred$se, col ="green3", lty =2, type ="o")
lines(pred$pred-2*pred$se, col ="purple", lty =3, type ="o")
acf(AR, main ="Simple Autocorrelation", ylim = c(-1,1), col ="black")
pacf(AR, main ="Partial Autocorrelation", ylim = c(-1,1), col ="black")
```


give the period = 7 to the model
```{r}
#order = p,d,q y seasonal = P,D,Q
model <- arima(LakeHuron, order=c(1,2,1), seasonal = list(order=c(2,1,0), period=7))
pred <- predict(model, n.ahead = 8)
pred

```

###plotting Data

```{r}

layout(matrix(c(1,1,2,3),2,2, byrow=TRUE))
plot(LakeHuron, xlim = c(1875, 1980), ylim = c(575,590), type ="o")
lines(pred$pred, col ="red", type ="o")
lines(pred$pred+2*pred$se, col ="green3", lty =2, type ="o")
lines(pred$pred-2*pred$se, col ="purple", lty =3, type ="o")
acf(AR, main ="Simple Autocorrelation", ylim = c(-1,1), col ="black")
pacf(AR, main ="Partial Autocorrelation", ylim = c(-1,1), col ="black")
```


whih one is the best model?We must do additional analysis