---
title: "Holt-winters and Errors"
author: "Armand"
date: "23 de julio de 2016"
output: html_document
---

#Holt-Winters Predictions

Load the data
```{r}

datos <- read.csv("C:/Users/Usuario/Desktop/promidat/series de tiempo/1/beer.csv", dec = ".")

colnames(datos)<- c("date", "cant")
head(datos)
```

Turn data into Ts
```{r}
#Convert data to ts
tbeer <- ts(datos[,2], frequency = 12, start =1956)
head(tbeer)

```

Holt-Winters
```{r}
beer.HS <- HoltWinters(tbeer)
beer.HS #HE calc alpha, beta and gamma

```

Plotting HW
```{r}
layout(1,1)
plot(beer.HS)

```

Predict
```{r}
pred <- predict(beer.HS, n.ahead = 10)

```

Plotting the Prediction
```{r}
plot(tbeer, las=1)
lines(pred, col = "red", lwd =2)
#another parameters for HW
beer.HS2 <- HoltWinters(tbeer, alpha = 0.12, beta = 0.65, gamma = 0.21)
lines(predict(beer.HS2, n.ahead = 10), col="navy", lwd =2.1)
panel.first = grid()
```


#Example with Airpass

```{r}
suppressMessages(library(itsmr))
head(airpass)

```

Convert Data into TS
```{r}
airpass <- ts(airpass, start=c(1949,1), frequency = 12)
plot(airpass, type ="o", col= "darkgreen")
```

Run HW (holt-winters)

```{r}
hw <- HoltWinters(airpass)
plot(hw)#The prediccion is in red

```
The prediction is in red

###Now we will predict 20 days
```{r}
plot(airpass)
lines(predict(hw, n.ahead = 20), col = "purple", lwd =2)
#model with others parameters
hw1 <- HoltWinters(airpass, alpha = 0.1, beta = 0.8, gamma = 0.1)
lines(predict(hw1, n.ahead = 20), col = "green")
panel.first =grid(nx =30)


```


#Measurement of Prediction Quality

Holt- Winters

Functions 
```{r}
ER <- function(pred, real){
  
  return (sum(abs(pred-real))/abs(sum(real)))
  
}

#mean square Error

ECM <- function(pred, real){
  
  N <- length(real)
  ss <- sum((real-pred)^2)
  return(ss/N)
  
}

PFA <- function(pred, real){
  total <- 0
  N <- length(pred)
  for (i in 1:N) {
    if(pred[i]>= real[i])
      total <- total +1
  }
  return(total/N)
}


PTFA <- function(pred, real){
  
  total <- 0
  sreal <- 0
  N <- length(pred)
  for (i in 1:N) {
    if(pred[i]>= real[i]){
      total <- total + (pred[i]-real[i])
      sreal <- sreal +abs(real[i])
      }
  }
  return(total/sreal)
}


```


#Example with ts beer

Load the data
```{r}

datos <- read.csv("C:/Users/Usuario/Desktop/promidat/series de tiempo/1/beer.csv", dec = ".")

colnames(datos)<- c("date", "cant")
head(datos)
```

Turn data into Ts
```{r}
#Convert data to ts
tbeer <- ts(datos[,2], frequency = 12, start =1956)
#Another ts for testing
beer.l <- tbeer[1:464]
beer.t <- tbeer[465:475]
beer.l <- ts(beer.l, frequency = 12, start =1956)
head(tbeer)

```

```{r}
length(beer.l)

```

Make the HW with learning data
```{r}
model <- HoltWinters(beer.l)
model
```

Plotting the Model
```{r}
plot(model)
```

The predictions

```{r}
pred <- predict(model, n.ahead = 11)
pred

```

The Relative Error
```{r}
ER(pred, beer.t)


```

The PFA Error
```{r}
PFA(pred, beer.t)

```

PTFA Error
```{r}
PTFA(pred, beer.t)

```

THE MSE
```{r}
sqrt(ECM(pred, beer.t))

```

###With another parameters
```{r}
model2 <- HoltWinters(beer.l, alpha =  0.02, beta = 0.9, gamma = 0.15)
model2
```

Plotting the Model
```{r}
plot(model2)
```

The predictions

```{r}
pred <- predict(model2, n.ahead = 11)
pred

```

The Relative Error
```{r}
ER(pred, beer.t)


```

The PFA Error
```{r}
PFA(pred, beer.t)

```

PTFA Error
```{r}
PTFA(pred, beer.t)

```

THE MSE
```{r}
sqrt(ECM(pred, beer.t))

```


##Example with box-jenkins

```{r}
suppressMessages(library(forecast))

```

The Auto ARIMA

```{r}
auto.arima(beer.l)

```

The parameter are ARIMA(1,1,0)(2,0,0) and period =12
```{r}
model <- arima(beer.l, order=c(1,1,0), seasonal = list(order=c(2,0,0), period=12))
pred <- predict(model, n.ahead = 11)
pred

```

##The ERRORS

The Relative Error
```{r}
ER(pred$pred, beer.t)


```

The PFA Error
```{r}
PFA(pred$pred, beer.t)

```

PTFA Error
```{r}
PTFA(pred$pred, beer.t)

```

THE MSE
```{r}
sqrt(ECM(pred$pred, beer.t))

```



#Function to calibrate models

```{r}

calibrate <- function(train, test){
  error.c <- Inf
  alpha.i <- 0.1
  while(alpha.i<=1){
    beta.i <- 0
    while(beta.i <=1){
    gamma.i <- 0
    while(gamma.i <=1){
      mod.i <- HoltWinters(train, alpha = alpha.i, beta = beta.i, gamma = gamma.i)
      pred.i <- predict(mod.i, n.ahead = length(test))
      error.i <- sqrt(ECM(pred.i, test))
      if(error.i < error.c){
        error.c <- error.i
        mod.c <- mod.i
      }
      gamma.i <- gamma.i + 0.1
      
      
    }
    beta.i <- beta.i+1
  }
    alpha.i <- alpha.i +1
  }
  
  return(mod.c)
  
}

```

Testting the Calibrate function
```{r}
model <- calibrate(beer.l, beer.t)
model

```



The predictions

```{r}
pred <- predict(model, n.ahead = 11)
pred

```

The Relative Error
```{r}
ER(pred, beer.t)


```

The PFA Error
```{r}
PFA(pred, beer.t)

```

PTFA Error
```{r}
PTFA(pred, beer.t)

```

THE MSE
```{r}
sqrt(ECM(pred, beer.t))

```


