---
title: "Time Series"
author: "Armand"
date: "20 de julio de 2016"
output: html_document
---


#Time Series

Stock data
```{r}
datos <- read.csv("stock.csv", header = T, dec = ".", sep =",")
head(datos)

```

Check de data

```{r}

summary(datos)

```
we have 6 time series


##Plotting data
```{r}
#plot the volume column
plot( datos[,6], type ="l", main = "Volume over time ")

```


#plottsing close data

```{r}
#plot the close column
plot( datos[,5], type ="l", main = "Close over time ")


```


#Plotting high price with low price


```{r}

#plot the high and low
plot( datos[,3], type ="l", main = "high vs low price over time ")
lines(datos[,4], type ="l", col="red")

```

##with ggplot

```{r}
library(ggplot2)
ggplot(datos) +xlab("index")+ylab("price")+ geom_line(data =datos, aes(y =High, x = c(1:length(High)) ), color ="red") + geom_line(data =datos, aes(y =Low, x = c(1:length(Low)) )) + ggtitle("Comparison High vs Low prices")


```



##Beer Example 


```{r}
datos_beer <- read.csv("beer.csv", dec = ".", sep =",")
head(datos_beer)
colnames(datos_beer) <- c("year", "cant")

```

##create the time series from data frame

```{r}
#Star year, month, freq = 1 data by month
beer <- ts(datos_beer[,2], start = c(1956,5), freq=12 )
beer

```


Plotting beer ts

```{r}
plot(beer, type ="l", col ="blue")


```



##Example with itsmr package

```{r}

library(itsmr)
head(airpass)

```

convert airpass to ts 

```{r}

airpass <- ts(airpass, start = c(1949, 1), freq = 12)
plot(airpass, type= "b", col = "pink")
 

```



#Time series:Preliminar Analysis

###Normal Test

```{r}
#with diff operator
#dataset stock
#this plot show atipicals
datos$Low <- as.numeric(datos$Low)

plot(diff(datos$Low), type ="l", col ="palegreen", main = "diff in time series ", xlim=c(0, 250), ylim = c(-2.5, 4))


```

###Ploting with Dates

```{r}
fechas <- strptime(as.character(datos$Date), "%Y-%m-%d")
#plot(x =fechas[-252], y = diff(datos$Low), xaxt="n", panel.first =grid(), type ="l", col ="palegreen", main = "diff in time series ")
plot(diff(datos$Low), xaxt="n", panel.first =grid(), type ="l", col ="palegreen", main = "diff in time series ", xlim=c(0, 250), ylim = c(-2.5, 4))

#axis.POSIXct(1, at = seq(as.Date(fechas[length(diff(datos$Low))]) ,as.Date(fechas[1]), by = "months"), format = "%m/%y")
#axis.POSIXct(1, at = seq(as.Date(fechas[length(diff(datos$Low))]), as.Date(fechas[1]),  "years"),labels = F, tcl = -0.2)



```




###making the normal test

1- make histogram  and density of differences
```{r}
difer <- diff(datos$Low)
hist(difer, prob = T, ylim=c(0,0.6) )
lines(density(diff(datos$Low)), lwd =2.5, col ="red")

```

2- Calculate mean
```{r}
mu <- mean(diff(datos$Low))
mu

```

3- Calculate sigma

```{r}

sigma <- sd (diff(datos$Low))
sigma
```

4- Vector x

```{r}

x <- seq(-4, 4, length=100)
x

```

5- plotting to see if diff follow the normal

```{r}

y <- dnorm(x, mu, sigma)
plot(x,y)
lines(x,y, lwd =2, col ="blue")
legend("topright", c("Histogram", "Density of Diff", "Normal"), lty = c(1,1), col = c("black", "red", "blue"), cex = .7)

```


#Linear smooth

Plotting Volumes
```{r}

fechas <- strptime(as.character(datos$Date), "%Y-%m-%d")
plot(datos$Volume,  panel.first =grid(), type ="l", col ="gray", main = "stock volume time series ", ylab = "Volume", xlab = "Dates")
axis.POSIXct(1, at = seq(as.Date(fechas[length((datos$Volume))]) ,as.Date(fechas[1]), by = "months"), format = "%m/%y")
axis.POSIXct(1, at = seq(as.Date(fechas[length((datos$Volume))]), as.Date(fechas[1]),  "years"),labels = F, tcl = -0.2)



```


smooth
```{r}
st.1 <- filter(datos$Volume, filter = rep(1/5,5))
st.2 <- filter(datos$Volume, filter = rep(1/25,25))
st.3 <- filter(datos$Volume, filter = rep(1/81,81))


```

Adding lines to the plot

```{r}
plot(st.1)
lines(st.1, col ="green3")
lines(st.2, col ="navy")
lines(st.3, col ="red")

#legend
legend("topright", c("Volumer Over time", "Filter1 5", "Filter2s 25", "Filter3 81"), lty = 1, col = c("gray", "green3","navy", "red"), cex = .8, box.col = 1, lwd =2)


```


#Serie Decomposition



```{r}
datos <- read.csv("beer.csv", dec = ".", sep =",")
head(datos)
colnames(datos) <- c("year", "cant")

```

```{r}
dim(datos)

```

Convert data to ts
```{r}

#Star year, month, freq = 1 data by month
beer <- ts(datos[,2], start = c(1956,5), freq=12 )
head(beer)

```

plotting the TS
```{r}

plot(beer)
```

Decomposition the TS

```{r}
#stl make decomposition
s <- stl(beer, s.window = "periodic")
head(s$time.series)

```

plotting the componenets of TS
```{r}
plot(s)

```



Example with stock data

```{r}
datos <- read.csv("stock.csv", header = T, dec = ".", sep =",")
head(datos)

```


convert volume to time serie

```{r}
#Star year, month, freq = 12 data by month
volume <- ts(datos[,6],  freq= 7 )
head(volume)


```

Decomposition the TS

```{r}
#stl make decomposition
s <- stl(volume, s.window = "periodic")
head(s$time.series)

```

plotting the componenets of TS
```{r}
plot(s, col="red")

```
