---
title: "series tiempo 2"
author: "Armand"
date: "21 de julio de 2016"
output: html_document
---


#Time Series 2


load data
```{r}

datos <- read.table("prostate.data", dec = ".")
head(datos)
```

##View the correlaction of data

```{r}
cor(datos)

```
the best is lcavol vs lpsa



make the regression lcavol vs lpsa

```{r}
model <- lm(lpsa~lcavol, datos)
model

```


Plotting data
```{r}

plot(lpsa~lcavol, datos)
abline(model, col="red")

```
red line is the regression line


###making the prediction

```{r}
pred <- predict(model, data.frame(lcavol=c(0.7,0.41,-0.23)), interval = "confidence")
pred

```



#Multiple Regression

```{r}

train <- (datos[datos$train,])
test <- (datos[!datos$train,])
model <- lm(lpsa ~lcavol + lweight,data= train)
model

```

Make the prediction

```{r}

pred2 <- predict(model, test)
pred2

```

Function the calculate the erros

```{r}
#RSS
RSS <- function(pred, real){
  ss <- sum((real-pred)^2)
  return (ss)
  
}

#RSE
RSE<- function(pred, real, numPre){
  
  N <- length(real)-numPre-1
  ss1 <- sqrt((RSS(pred, real))/N)
  return (ss1)
  
}

#MSE
MSE <- function(pred, real){
  
  N <- length(real)
  ss <- (1/N)*RSS(pred, real)
  return (ss)
  
  
}

#Relative Error

ErrorRelative <- function(pred, real){
  
  ss <- sum(abs(real-pred))/sum(abs(real))
  return (ss)
}

```



#Evaluating Errors


```{r}

summary(model)

```

##Errors

```{r}

RSE(pred2, test$lpsa,2)

```
Note: for this values option confidence in lm can not be activated

```{r}

MSE(pred2, test$lpsa)


```

```{r}

ErrorRelative(pred2, test$lpsa)

```



#Ridge Regression

```{r}
suppressMessages(library(glmnet))
#build matraxi for glmnet i.e quit to predict variable
x <- model.matrix(lpsa~.,train)
head(x)

```

column 1 must be eliminated
```{r}

x <- model.matrix(lpsa~., train)[,-1]
head(x)
```


extrac the variable to predict
```{r}
y <- train$lpsa


```

Build testting table 
```{r}
test.table <- model.matrix(lpsa~.,test)[,-1]

```

###Making the ridge regression

```{r}

ridge.mod <- glmnet(x,y, alpha =0)

```

Plottting the regression
```{r}

plot(ridge.mod, "lambda", label=T)
panel.first = grid( lty = 3, lwd = 1)

```

###the coef with lambda big
the coefs are small
```{r}
coef(ridge.mod)[,5]

```


###the coefs with lambda small
the coefs are bigger
```{r}
coef(ridge.mod)[,98]
```


findinf the optimal lambda with CV
```{r}
dat.cv <- cv.glmnet(x,y, alpha=0)
plot(dat.cv)

```
we can see the optimal lambda es between -2 to 0


the value of lambda will be
```{r}
best.lambda <- dat.cv$lambda.min
best.lambda

```



##Prediction with the best lambda

```{r}

pred <- predict(ridge.mod, s = best.lambda, newx = test.table)
#MSE 

MSE(pred, test$lpsa)
```


Relative Error
```{r}

ErrorRelative(pred, test$lpsa)

```

#Lasso Regression

with the same data
```{r}

lasso.mod <- glmnet(x,y, alpha = 1)

```

###Plotting  the regression

```{r}

plot(lasso.mod, "lambda", label = T)
panel.first = grid( lty = 3, lwd = 1)

```


###the coef with lambda big
the coefs are small
```{r}
coef(lasso.mod)[,5]

```


###the coefs with lambda small
the coefs are bigger
```{r}
coef(lasso.mod)[,70]
```


findinf the optimal lambda with CV
```{r}
dat.cv <- cv.glmnet(x,y, alpha=1)
plot(dat.cv)

```
we can see the optimal lambda es between -5 to -2


the value of lambda will be
```{r}
best.lambda <- dat.cv$lambda.min
best.lambda

```



##Prediction with the best lambda

```{r}

pred <- predict(lasso.mod, s = best.lambda, newx = test.table)
#MSE 

MSE(pred, test$lpsa)
```


Relative Error
```{r}

ErrorRelative(pred, test$lpsa)

```



#Logistic Refression

load data
```{r}

train <- read.table("C:/Users/Usuario/Desktop/promidat/predictivos/MuestraAprendizajeCredito2500.csv", sep = ";", header = T)
test <- read.table("C:/Users/Usuario/Desktop/promidat/predictivos/MuestraTestCredito2500.csv", sep = ";", header = T)

head(train)
```

Make the logistic model
```{r}
model <- glm(BuenPagador~., data = train, family = binomial)
model
 
```

Look at the probabilities

```{r}
prob <- predict(model, test, type ="response")
head(prob)

```


To Verify
```{r}
#packet turn into o and 1, 1 = si
contrasts(train$BuenPagador)
```

##Making the Prediction
We must Build the Rules of prediction
```{r}
prediction <- rep("No", dim(test)[1])
head(prediction)

```

Building the Rules of prediction
```{r}
prediction[prob > 0.5] = "Si"
actual <- test$BuenPagador

```

Confusion Matrix

```{r}
MC <- table(actual, prediction)
MC

```

Error and success
```{r}
success <- (sum(diag(MC)))/sum(MC)
success

```

```{r}
error <- 1 -success
error

```


#Fourier series



Load data 
```{r}

datos <- read.csv("C:/Users/Usuario/Desktop/promidat/series de tiempo/1/beer.csv", dec = ".")

colnames(datos)<- c("date", "cant")
head(datos)
```


Take the log of beer cant

```{r}
lbeer <- log(datos[,2]) 
t<- seq(1956, 1995.2, length= length(datos[,2]))

```

Plotting the lbeer data
```{r}
plot(t, lbeer, type = "o")

```


###Regression for the trends
```{r}

t2 <- t^2
plot(t, lbeer, type = "o")
lines(t, lm(lbeer~t+t2)$fit, col=2, lwd =2)

```

###Fourier for the periods
Addind fouroes series to the model
```{r}
sin.t <- sin(2*pi*t)
cos.t <- cos(2*pi*t)
plot(t, lbeer, type = "o")
lines(t, lm(lbeer~t+t2)$fit, col=2, lwd =2)
lines(t, lm(lbeer~t+t2+sin.t+cos.t)$fit, col = 3, lwd =2)

```


Peridogram
```{r}
#Convert data to ts
tbeer <- ts(datos[,2], frequency = 12, start =1956)
res <- spec.pgram(tbeer, log = "no")
res

```

order the data to find the max spec
```{r}
order(res$spec, res$freq, decreasing = T)

```
max spec ocurrs in freq = 40, second in 2, third in 120

```{r}
max1 <- res$freq[40]
max1

```

max2
```{r}
max2 <- res$freq[2]
max2

```

max3
```{r}
max3 <- res$freq[120]
max3

```


###Plotting Peridogram

```{r}


plot(res$freq,res$spec)


```


the  first peak ocurre in 1 (from table order)
```{r}
plot(res$freq,res$spec)
abline(v=max1, lty ="dotted", col ="red")
# the 12 is from frecuency
period1 <- 12/max1
period1
```


the  second peak ocurre in 0.005
```{r}
plot(res$freq,res$spec)
abline(v=max1, lty ="dotted", col ="red")
abline(v=max2, lty ="dotted", col ="blue")
period2 <- 12/max2
period2
```



the third peak ocurre in 3
```{r}
plot(res$freq,res$spec)
abline(v=max1, lty ="dotted", col ="red")
abline(v=max2, lty ="dotted", col ="blue")
abline(v=max3, lty ="dotted", col ="green2")
period3 <- 12/max3
period3
```

