---
title: "Calibration predictive methods"
author: "Armand"
date: "14 de julio de 2016"
output: html_document
---



# K-nn


load the Data
```{r }
library(kknn)
datos <- read.csv("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/iris.csv", sep = ";", dec = ".", header = TRUE)

#Generamos muestra al azar
muestra<- sample(1:150, 50)
#tabla de testing
ttesting<-datos[muestra,]
#tabla de aprendizake
taprendiz <- datos[-muestra,]

#implementamos el modelo
modelo <- train.kknn(tipo ~., data= taprendiz, kmax = 9)
modelo

```

## Evaluation ofs Knn

Performing the prediction:

```{r }
prediction<- predict(modelo, ttesting[,-5])
head(prediction)

```


the confusion matrix

```{r }
matriz.conf<- table(ttesting[,5], prediction)
matriz.conf


```

Hit percentage

```{r }
aciertos<- sum(diag(matriz.conf))/sum(matriz.conf)
aciertos

```

The error:

```{r }
error<- 1 - aciertos
error

```


#Example with scoring file

Cargamos los datos
```{r }
library(kknn)
datos <- read.csv("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/MuestraAprendizajeCredito2500.csv", sep = ";", dec = ".", header = TRUE)
ttesting <- read.table("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/MuestraTestCredito2500.csv", sep = ";", header = TRUE)

dim(datos)

#tabla de aprendizake
taprendiz <- datos

```

Transforming the Variables

```{r }

taprendiz$MontoCredito <- as.factor(taprendiz$MontoCredito)
taprendiz$IngresoNeto <- as.factor(taprendiz$IngresoNeto)
taprendiz$CoefCreditoAvaluo <- as.factor(taprendiz$CoefCreditoAvaluo)
taprendiz$MontoCuota <-  as.factor(taprendiz$MontoCuota)
taprendiz$GradoAcademico <- as.factor(taprendiz$GradoAcademico)
taprendiz$BuenPagador <- as.factor(taprendiz$BuenPagador)

#convertimos la de la tabla de testing
ttesting$MontoCredito <- as.factor(ttesting$MontoCredito)
ttesting$IngresoNeto <- as.factor(ttesting$IngresoNeto)
ttesting$CoefCreditoAvaluo <- as.factor(ttesting$CoefCreditoAvaluo)
ttesting$MontoCuota <- as.factor(ttesting$MontoCuota)
ttesting$GradoAcademico <- as.factor(ttesting$GradoAcademico)
ttesting$BuenPagador <- as.factor(ttesting$BuenPagador)
```


implementing the model
```{r}
#implementamos el modelo
modelo <- train.kknn(BuenPagador ~ ., data= taprendiz, kmax = 5)
modelo

```


Performing the Prediction:

```{r }
prediction<- predict(modelo, ttesting[,-6])
head(prediction)

```


the confusion matrix

```{r }
matriz.conf<- table(ttesting[,6], prediction)
matriz.conf


```

Hits

```{r }
aciertos<- sum(diag(matriz.conf))/sum(matriz.conf)
aciertos

```

and the error:

```{r }
error<- 1 - aciertos
error

```


#NAIVES BAYES

Loadinfg the Data
```{r }
library(e1071)
datos <- read.csv("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/iris.csv", sep = ";", dec = ".", header = TRUE)
head(datos)
```

##the modelo is made
```{r}
#Generamos muestra al azar
muestra<- sample(1:150, 50)
#tabla de testing
ttesting<-datos[muestra,]
#tabla de aprendizake
taprendiz <- datos[-muestra,]

#implementamos el modelo
modelo <-naiveBayes(tipo ~., data= taprendiz)
modelo

```


¨Performing the Prediction:

```{r }
prediction<- predict(modelo, ttesting[,-5])
head(prediction)

```


#the confusion matrix

```{r }
matriz.conf<- table(ttesting[,5], prediction)
matriz.conf


```

Hits

```{r }
aciertos<- sum(diag(matriz.conf))/sum(matriz.conf)
aciertos

```

Error:

```{r }
error<- 1 - aciertos
error

```



#Example Bayes with another data

load the data
```{r }
library(kknn)
datos <- read.csv("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/MuestraAprendizajeCredito2500.csv", sep = ";", dec = ".", header = TRUE)
ttesting <- read.table("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/MuestraTestCredito2500.csv", sep = ";", header = TRUE)

dim(datos)

#tabla de aprendizake
taprendiz <- datos

```




Transforming the variables 

```{r }

taprendiz$MontoCredito <- as.factor(taprendiz$MontoCredito)
taprendiz$IngresoNeto <- as.factor(taprendiz$IngresoNeto)
taprendiz$CoefCreditoAvaluo <- as.factor(taprendiz$CoefCreditoAvaluo)
taprendiz$MontoCuota <-  as.factor(taprendiz$MontoCuota)
taprendiz$GradoAcademico <- as.factor(taprendiz$GradoAcademico)
taprendiz$BuenPagador <- as.factor(taprendiz$BuenPagador)

#convertimos la de la tabla de testing
ttesting$MontoCredito <- as.factor(ttesting$MontoCredito)
ttesting$IngresoNeto <- as.factor(ttesting$IngresoNeto)
ttesting$CoefCreditoAvaluo <- as.factor(ttesting$CoefCreditoAvaluo)
ttesting$MontoCuota <- as.factor(ttesting$MontoCuota)
ttesting$GradoAcademico <- as.factor(ttesting$GradoAcademico)
ttesting$BuenPagador <- as.factor(ttesting$BuenPagador)
```



Making the model
```{r}
#implementamos el modelo
modelo <- naiveBayes(BuenPagador ~ ., data= taprendiz)
modelo

```


Performing the prediccion:

```{r }
prediction<- predict(modelo, ttesting[,-6])
head(prediction)

```


the confusion matrix

```{r }
matriz.conf<- table(ttesting[,6], prediction)
matriz.conf


```

Hits Percentage

```{r }
aciertos<- sum(diag(matriz.conf))/sum(matriz.conf)
aciertos

```

The error:

```{r }
error<- 1 - aciertos
error
```


#Support Vector Machine Model


Load the data
```{r }
library(e1071)
library(class)
datos <- read.csv("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/iris.csv", sep = ";", dec = ".", header = TRUE)
head(datos)
```

```{r}
summary(datos)

```

The samples are generated
```{r}

#Generamos muestra al azar
muestra<- sample(1:150, 50)
#tabla de testing
ttesting<-datos[muestra,]
#tabla de aprendizake
taprendiz <- datos[-muestra,]

```

##Build The Model

```{r}

#implementamos el modelo
modelo <- svm(tipo ~., data= taprendiz, kernel= "linear")
modelo

```



Performs The Prediction:

```{r }
prediction<- predict(modelo, ttesting)
head(prediction)

```

the confusion matrix
```{r }
matriz.conf<- table(ttesting[,5], prediction)
matriz.conf


```

Hist Percentage
```{r }
aciertos<- sum(diag(matriz.conf))/sum(matriz.conf)
aciertos

```

The error:

```{r }
error<- 1 - aciertos
error
```


##in order to ploting we build the model again but with only 2 vars

```{r}

#implementamos el modelo
modelo <- svm(tipo  ~ s.largo + s.ancho, data= taprendiz, kernel= "linear")
modelo

```

Ploting
```{r}

plot(modelo, datos, s.ancho~s.largo, slice = list(s.ancho=1, s.largo=2))

```



#Example SVM with another data

load the data
```{r }
library(kknn)
datos <- read.csv("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/MuestraAprendizajeCredito2500.csv", sep = ";", dec = ".", header = TRUE)
ttesting <- read.table("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/MuestraTestCredito2500.csv", sep = ";", header = TRUE)

dim(datos)

#tabla de aprendizake
taprendiz <- datos

```




Transform the Variables

```{r }

taprendiz$MontoCredito <- as.factor(taprendiz$MontoCredito)
taprendiz$IngresoNeto <- as.factor(taprendiz$IngresoNeto)
taprendiz$CoefCreditoAvaluo <- as.factor(taprendiz$CoefCreditoAvaluo)
taprendiz$MontoCuota <-  as.factor(taprendiz$MontoCuota)
taprendiz$GradoAcademico <- as.factor(taprendiz$GradoAcademico)
taprendiz$BuenPagador <- as.factor(taprendiz$BuenPagador)

#convertimos la de la tabla de testing
ttesting$MontoCredito <- as.factor(ttesting$MontoCredito)
ttesting$IngresoNeto <- as.factor(ttesting$IngresoNeto)
ttesting$CoefCreditoAvaluo <- as.factor(ttesting$CoefCreditoAvaluo)
ttesting$MontoCuota <- as.factor(ttesting$MontoCuota)
ttesting$GradoAcademico <- as.factor(ttesting$GradoAcademico)
ttesting$BuenPagador <- as.factor(ttesting$BuenPagador)
```


Build the model
```{r}
#implementamos el modelo
modelo <- svm(BuenPagador ~ ., data= taprendiz, kernel="linear")
modelo

```


The Prediction
```{r }
prediction<- predict(modelo, ttesting)
head(prediction)

```


the confusion matrix
```{r }
matriz.conf<- table(ttesting[,6], prediction)
matriz.conf


```

Hits Percentage
```{r }
aciertos<- sum(diag(matriz.conf))/sum(matriz.conf)
aciertos

```

The error:

```{r }
error<- 1 - aciertos
error
```




#Decision Tree


Load the Data
```{r }
library(rpart)
library(rpart.plot)
datos <- read.csv("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/iris.csv", sep = ";", dec = ".", header = TRUE)
head(datos)
```

Build  the Model
```{r}

modelo <- rpart(tipo~., data = datos)
modelo

```



Perform the Prediction
```{r }
prediction<- predict(modelo, datos, type = "class")
head(prediction)

```


the confusion matrix
```{r }
matriz.conf<- table(datos[,5], prediction)
matriz.conf


```

Hits
```{r }
aciertos<- sum(diag(matriz.conf))/sum(matriz.conf)
aciertos

```

The error:

```{r }
error<- 1 - aciertos
error
```


Ploting
```{r}
plot(modelo)
text(modelo)

```

#Ploting with Rpart.plot

```{r}

prp(modelo, extra=104, branch.type = 2, box.col = c("pink", "palegreen", "blue")[modelo$frame$yval] )

```



#DT with another data


Load the Data
```{r }
library(kknn)
datos <- read.csv("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/MuestraAprendizajeCredito2500.csv", sep = ";", dec = ".", header = TRUE)
ttesting <- read.table("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/MuestraTestCredito2500.csv", sep = ";", header = TRUE)

dim(datos)

#tabla de aprendizake
taprendiz <- datos

```



Transform the data
```{r }

taprendiz$MontoCredito <- as.factor(taprendiz$MontoCredito)
taprendiz$IngresoNeto <- as.factor(taprendiz$IngresoNeto)
taprendiz$CoefCreditoAvaluo <- as.factor(taprendiz$CoefCreditoAvaluo)
taprendiz$MontoCuota <-  as.factor(taprendiz$MontoCuota)
taprendiz$GradoAcademico <- as.factor(taprendiz$GradoAcademico)
taprendiz$BuenPagador <- as.factor(taprendiz$BuenPagador)

#convertimos la de la tabla de testing
ttesting$MontoCredito <- as.factor(ttesting$MontoCredito)
ttesting$IngresoNeto <- as.factor(ttesting$IngresoNeto)
ttesting$CoefCreditoAvaluo <- as.factor(ttesting$CoefCreditoAvaluo)
ttesting$MontoCuota <- as.factor(ttesting$MontoCuota)
ttesting$GradoAcademico <- as.factor(ttesting$GradoAcademico)
ttesting$BuenPagador <- as.factor(ttesting$BuenPagador)
```



The Model
```{r}

modelo <- rpart(BuenPagador~., data = taprendiz)
modelo

```


Prediction;
```{r }
prediction<- predict(modelo, ttesting, type = "class")
head(prediction)

```


the confusion matrix
```{r }
matriz.conf<- table(ttesting[,6], prediction)
matriz.conf


```

Hits Percentage
```{r }
aciertos<- sum(diag(matriz.conf))/sum(matriz.conf)
aciertos

```

error:

```{r }
error<- 1 - aciertos
error
```


Ploting
```{r}
plot(modelo)
text(modelo)

```

```{r}

prp(modelo, extra=104, branch.type = 2, box.col = c("pink", "palegreen", "blue")[modelo$frame$yval] )

```




#Random Forest


Load the Data
```{r }
library(randomForest)
datos <- read.csv("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/iris.csv", sep = ";", dec = ".", header = TRUE)
head(datos)
```

```{r}
summary(datos)

```

making the Samples
```{r}

#Generamos muestra al azar
muestra<- sample(1:150, 50)
#tabla de testing
ttesting<-datos[muestra,]
#tabla de aprendizake
taprendiz <- datos[-muestra,]

```



Build the Model
```{r}

modelo <- randomForest(tipo~., data = taprendiz, importance= TRUE)
modelo

```


Perform the Prediction
```{r }
prediction<- predict(modelo, ttesting, type = "class")
head(prediction)

```


the confusion matrix
```{r }
matriz.conf<- table(ttesting[,5], prediction)
matriz.conf


```

Hits Percentage
```{r }
aciertos<- sum(diag(matriz.conf))/sum(matriz.conf)
aciertos

```

Error:

```{r }
error<- 1 - aciertos
error
```



#Booting Methods, i.e ADA

Load the Data
```{r }
library(ada)
datos <- read.csv("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/MuestraAprendizajeCredito2500.csv", sep = ";", dec = ".", header = TRUE)
ttesting <- read.table("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/MuestraTestCredito2500.csv", sep = ";", header = TRUE)

dim(datos)

#tabla de aprendizake
taprendiz <- datos

```



Transform the Data
```{r }

taprendiz$MontoCredito <- as.factor(taprendiz$MontoCredito)
taprendiz$IngresoNeto <- as.factor(taprendiz$IngresoNeto)
taprendiz$CoefCreditoAvaluo <- as.factor(taprendiz$CoefCreditoAvaluo)
taprendiz$MontoCuota <-  as.factor(taprendiz$MontoCuota)
taprendiz$GradoAcademico <- as.factor(taprendiz$GradoAcademico)
taprendiz$BuenPagador <- as.factor(taprendiz$BuenPagador)

#convertimos la de la tabla de testing
ttesting$MontoCredito <- as.factor(ttesting$MontoCredito)
ttesting$IngresoNeto <- as.factor(ttesting$IngresoNeto)
ttesting$CoefCreditoAvaluo <- as.factor(ttesting$CoefCreditoAvaluo)
ttesting$MontoCuota <- as.factor(ttesting$MontoCuota)
ttesting$GradoAcademico <- as.factor(ttesting$GradoAcademico)
ttesting$BuenPagador <- as.factor(ttesting$BuenPagador)
```


Make the Model
```{r}

modelo <- ada(BuenPagador~., data = taprendiz, iter=100, nu=1, type= "discrete")
modelo

```


Perform the Prediction
```{r }
prediction<- predict(modelo, ttesting)
head(prediction)

```

Create the confusion matrix
```{r }
matriz.conf<- table(ttesting[,6], prediction)
matriz.conf


```

hits Percentage
```{r }
aciertos<- sum(diag(matriz.conf))/sum(matriz.conf)
aciertos

```

Error:

```{r }
error<- 1 - aciertos
error
```

Ploting the Results
```{r}
plot(modelo, TRUE,TRUE)

```

##Best Variables

```{r}
varplot(modelo)

```




#Neural Networks examples


Load the data
```{r }
library(nnet)
datos <- read.csv("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/iris.csv", sep = ";", dec = ".", header = TRUE)
head(datos)
```

```{r}
summary(datos)

```

Made the samples
```{r}

#Generamos muestra al azar
muestra<- sample(1:150, 50)
#tabla de testing
ttesting<-datos[muestra,]
#tabla de aprendizake
taprendiz <- datos[-muestra,]

```


Create the model
```{r}

modelo <- nnet(tipo~., data = taprendiz, size=4, rang= 0.1, decay=5e-4, maxit=200, trace= FALSE)
modelo

```


The Prediction
```{r }
prediction<- predict(modelo, ttesting[,-5], type = "class")
head(prediction)

```


Create the confusion matrix
```{r }
matriz.conf<- table(ttesting[,5], prediction)
matriz.conf


```

Hits Percentage
```{r }
aciertos<- sum(diag(matriz.conf))/sum(matriz.conf)
aciertos

```

The error:

```{r }
error<- 1 - aciertos
error
```




#Save the model on the drive for later :) 


Load the Datas
```{r }
library(nnet)
datos <- read.csv("C:/Users/Usuario/Desktop/promidat/calibracion_y_seleccion/2/iris.csv", sep = ";", dec = ".", header = TRUE)
head(datos)
```

```{r}
summary(datos)

```

the samples are generated
```{r}

#Generamos muestra al azar
muestra<- sample(1:150, 50)
#tabla de testing
ttesting<-datos[muestra,]
#tabla de aprendizake
taprendiz <- datos[-muestra,]

```


Build the model

```{r}

modelo <- nnet(tipo~., data = taprendiz, size=4, rang= 0.1, decay=5e-4, maxit=20, trace= FALSE)
modelo

```


#save

```{r}
save(modelo, file = "modelos_redes_iris.rda")

```

#We can retrieve our model with load

```{r}
load("modelos_redes_iris.rda")

```



The Prediction:

```{r }
prediction<- predict(modelo, ttesting[,-5], type = "class")
head(prediction)

```

the confusion matrix
```{r }
matriz.conf<- table(ttesting[,5], prediction)
matriz.conf


```

hits Percentages
```{r }
aciertos<- sum(diag(matriz.conf))/sum(matriz.conf)
aciertos

```

Error:

```{r }
error<- 1 - aciertos
error
```


